Interpretable Neural Networks using EAGGA

### 2025-03-13 paper/main.tex
add plots

\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
%\blindtext
\end{abstract}

@@

\section{Experimental Results and Discussion}

@@

>>>>

\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
%\blindtext
- propose a network architecture specifically suited for the EAGGA algorithm
- achieve comparable performance as training XGBoost with EAGGA
\end{abstract}

@@

\section{Experimental Results and Discussion}
\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{../code/export/plot_test_dhvs.png}  % scale figure, cf. https://tex.stackexchange.com/a/16584
  \caption{caption}
  \label{fig-test-dhvs}
\end{figure}

@@

\section{}
\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{../code/export/plot_early_stopping_losses_pareto_set.png}
  \caption{caption}
  \label{fig-es-losses}
\end{figure}

\section{}
\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{../code/export/plot_val_dhvs_over_time.png}
  \caption{caption}
  \label{fig-val-dhvs}
\end{figure}
